{[}DRAFT, please don't distribute{]} Wildcard: a tool for modifying websites by directly manipulating data tables

### 2019-12-28 paper.tex
more tweaks
add a conditional rendering plugin for html and pdf

\title{Wildcard: a tool for modifying websites by directly manipulating
data tables}
\subtitle{}% optional

@@

@@

For example, here we open up a table view that corresponds to search
results on the Airbnb travel site.

@@

>>>>

\title{{[}DRAFT, please don't distribute{]} Wildcard: a tool for
modifying websites by directly manipulating data tables}
\subtitle{}% optional

@@

Do somes tuff

@@

@@

For example, in Fig.~\ref{fig:table} we open up a table view that
corresponds to search results on the Airbnb travel site.

\begin{figure}
\hypertarget{fig:table}{%
\centering
\includegraphics{media/opentable.png}
\caption{Opening a table corresponding to search results on
Airbnb}\label{fig:table}
}
\end{figure}
